Estimating Correspondences of Deformable Objects ``In-the-wild"

### 2015-11-06 contents/evaluation.tex
Updates from ShareLaTeX

We evaluate the performance of the proposed methodology in experiments of estimating correspondences of human poses in-the-wild and in non-rigid object alignment in-the-wild.  For further experimental results and visualisations please refer to our supplementary material.

@@

\subsection{Non-rigid Object Alignment In-the-wild}
\label{exp:daam_benchmark}

This experiment compares the fitting accuracy of dense Active Appearance Models (dAAMs) trained with the proposed framework, as compared to classic AAMs. We here consider two object classes that have rich interior textures: faces and ears. The comparisons are for the problem of non-rigid face and ear alignment in-the-wild.

\paragraph{Databases \& Error Metrics} For face experiment, both models were built using the 811 training images of the Labelled Faces Parts in-the-Wild (LFPW) \cite{Asthana2014} database. Classic AAM were built from 68 point landmark annotations using the standard procedure described in \cite{Cootes2001,Matthews2004}; piecewise affine was used as their motion model. Our dAAMs were built as the pipeline proposed. Results for this experiment are reported over the 224 testing images of the LFPW database using again 68 point ground truth landmark annotations. For this experiment, we report results using pixels intensities (INT) for both models.

@@

\subsection{Arm Pose Estimation}
\label{exp:benchmark}
This section provides experiments showing that training patch-based AAM from outline annotation provides remarkable joints estimation.

Experiments \ref{exp:benchmark} compare joints localisation accuracy of our skeleton prediction from outline fitting with respect to that of state-of-the-art human pose estimation algorithms in-the-wild. In addition, the experiment investigates the impact of annotating outlines of human poses instead of annotating skeletons. Note that all results reported in this section were obtained by fitting patch-based AAM using the fast version of the Simultaneous Inverse Compositional algorithm (Fast-SIC) originally proposed by the authors of \cite{Papandreou2008}.

\paragraph{Dataset \& Error Metric} There are significant numbers of datasets exist for human pose estimation, where FLIC\cite{sapp2013modec}, BBC Pose\cite{pfister2015flowing}, Fashion Pose\cite{dantone2013human} and MPII\cite{andriluka14cvpr} attracted most public attention. In our work, we reported our performance comparison on BBC Pose Dataset\cite{pfister2015flowing}, which has relatively most consistent skeleton annotation among the others.

>>>>

We evaluate the performance of the proposed methodology for the task of human body pose correspondence estimation, as well as non-rigid alignment ``in-the-wild''. For further experimental results, please refer to the supplementary material.

@@

\subsection{Non-rigid Object Alignment In-the-wild}
\label{exp:daam_benchmark}
Herein, we compare the fitting accuracy of the dAAMs that are trained with our proposed framework with holistic sparse AAMs~\cite{Cootes2001,Matthews2004}. We consider two object classes that demonstrate rich texture: face and ear.

\paragraph{Databases \& Error Metrics} In the case of face, we build both models using the 811 training images of the Labelled Faces Parts in-the-Wild (LFPW) \cite{belhumeur2013localizing}. Sparse AAMs were built from the 68 points annotations provided by~\cite{sagonas_iccv_300w_2013}. We use the standard formulation described in~\cite{Cootes2001,Matthews2004}; piecewise affine was used as their motion model. Our dAAMs were built as the pipeline proposed. Results for this experiment are reported over the 224 testing images of the LFPW database using again 68 point ground truth landmark annotations. For this experiment, we report results using pixels intensities (INT) for both models.

@@

\subsection{Arm Pose Estimation}
\label{exp:benchmark}

This experiment evaluates the localisation of arm joints using our skeleton prediction from outline fitting and compares it to state-of-the-art human pose estimation algorithms in-the-wild. 
% We show here that training a patch-based AAM from our automatic outline annotations provides remarkable joints estimation.
In addition, the experiment investigates the impact of annotating outlines of human poses instead of annotating skeletons. Note that all results reported in this section were obtained by fitting patch-based AAM using the fast version of the Simultaneous Inverse Compositional algorithm (Fast-SIC) originally proposed by the authors of \cite{Papandreou2008}.

\paragraph{Dataset \& Error Metric} There exist several datasets for human pose estimation, with FLIC \cite{sapp2013modec}, BBC Pose \cite{pfister2015flowing}, Fashion Pose \cite{dantone2013human} and MPII \cite{andriluka14cvpr} being some of the most commonly-used ones. In this work, we report quantitative evaluation on BBC Pose, which contains the most consistent skeleton annotations among the relevant datasets.

### 2015-11-06 contents/implementation.tex
citation fix, label fix
Updates from ShareLaTeX

@@

Let $\bm{d}(\bx;n)$, $\bm{d}(\bx;0):\Omega\rightarrow \R^{N_c}$ be the $n$-th training SVS image and the reference SVS image respectively. Following \cite{Garg:2013hu}, we propose to estimate the shape flow over all training images by minimizing the following energy:
\begin{align}
E_{sf} & =\alpha
\int_{\Omega}\sum_{n=1}^{N_t} \|\bm{d}(\bx+\bm{u}_n(x);n)-\bm{d}(x;0)\| \ud \bx \label{eq:costfunc}\\
    &+ \beta \int_{\Omega}\sum_{n=1}^{N_t}\|\bm{u}_n(\bx)-\sum_{i=1}^R\bm{q}_i(n)\bm{v}_i(\bx)\|^2 \ud \bx \label{eq:lowrank}\\
    &+
\int_\Omega  \sum_{i=1}^R \,\, \left \|    \nabla \bm{v}_i(\bx)    \right \|  \,\ud \bx \label{eq:TVterm}
\end{align}
This energy consists of two sets of unknown shape flows that are relatively close to each other: (i) $\bm{u}_n(x)$ which tries to explain the data from the input SVS images, and (ii) the shape flow determined by the correspondence basis coefficients $\bm{v}_i(\bx)$ that are spatially regularised and enforce a low-rank prior. We minimize this energy jointly with respect to $\bm{u}_n(\bx)$ and $\bm{v}_i(\bx)$. The positive parameters $\alpha$ and $\beta$ weigh the balance between the terms of the energy.

@@

We implement the minimization of the energy $E_{sf}$ by using the optimization algorithm described in \cite{Garg:2013hu} \footnote{We used the publicly available code at \url{http://bitbucket.org/troussos/mfsf/}}.
We slightly modify this algorithm so that, instead of initialising the coarse-to-fine and warping iterations with a zero flow, we use Thin Plate Splines (TPS) \cite{Bookstein1989} interpolation of the initial correspondence vectors described in Step~\ref{sec:step2}.
This yields a significantly better initial location of the highly-nonconvex objective function and improves the computational efficiency, since much less coarse-to-fine pyramids are needed.
%
Figure~\ref{fig:deformationfield} shows some examples of deformation fields derived from the estimated shape flow computed by the aforementioned method. These results correspond to exemplar training shapes in the case of an arm dataset. We observe that the shape flow estimation captures the shape and deformations of the human arm in a plausible way.

@@

\begin{figure}[b!]
    \centering
    \includegraphics[width=0.45\textwidth]{resources/models}
    \caption{Exemplar dense shape models build for faces and ears. Dense shapes are presented as grid for better visualisation.}
    \label{fig:dense_models}
\end{figure}

>>>>

\begin{figure}[b!]
    \centering
    \includegraphics[width=0.4\textwidth]{resources/models}
    \caption{Exemplar dense shape models build for faces and ears. Dense shapes are presented as grid for better visualisation.}
    \label{fig:dense_models}
\end{figure}

\begin{figure*}[t!]
\begin{center}
 \begin{tabular}{ccc}
\subfigure[]{
    \newcommand{\flowh}{0.12\columnwidth}
    \includegraphics[height=\flowh]{resources/Fig_Flows/1}
    \includegraphics[height=\flowh]{resources/Fig_Flows/2}
    \includegraphics[height=\flowh]{resources/Fig_Flows/3}
    \includegraphics[height=\flowh]{resources/Fig_Flows/4}
    \includegraphics[height=\flowh]{resources/Fig_Flows/5}
    \includegraphics[height=\flowh]{resources/Fig_Flows/6}
} &
\subfigure[]{
    \includegraphics[width=0.2\textwidth]{resources/models}
}
 \end{tabular}
\end{center}
\caption{(a) . (b) }
\label{REC}
\end{figure*}

@@

Let $\bm{d}(\bx;n)$, $\bm{d}(\bx;0):\Omega\rightarrow \R^{N_c}$ be the $n$-th training SVS image and the reference SVS image respectively. Following \cite{Garg:2013hu}, we propose to estimate the shape flow over all training images by minimizing the following energy:
\begin{align}
E_{sf} & =\alpha
\int_{\Omega}\sum_{n=1}^{N_t} \|\bm{d}(\bx+\bm{u}_n(x);n)-\bm{d}(x;0)\| \ud \bx \label{eq:costfunc}\\
    &+ \beta \int_{\Omega}\sum_{n=1}^{N_t}\|\bm{u}_n(\bx)-\sum_{i=1}^R\bm{q}_i(n)\bm{v}_i(\bx)\|^2 \ud \bx \label{eq:lowrank}\\
    &+
\int_\Omega  \sum_{i=1}^R \,\, \left \|    \nabla \bm{v}_i(\bx)    \right \|  \,\ud \bx \label{eq:TVterm}
\end{align}
This energy consists of two sets of unknown shape flows that are relatively close to each other: (i) $\bm{u}_n(x)$ which tries to explain the data from the input SVS images, and (ii) the shape flow determined by the correspondence basis coefficients $\bm{v}_i(\bx)$ that are spatially regularised and enforce a low-rank prior. 
%We minimize this energy jointly with respect to $\bm{u}_n(\bx)$ and $\bm{v}_i(\bx)$. 
The positive parameters $\alpha$ and $\beta$ weigh the balance between the terms of the energy.

@@

We implement the minimization of the energy $E_{sf}$ by using the optimization algorithm described in \cite{Garg:2013hu}. For more details, please refer to the Supplementary Material.
%We slightly modify this algorithm so that, instead of initialising the coarse-to-fine and warping iterations with a zero flow, we use Thin Plate %Splines (TPS) \cite{Bookstein1989} interpolation of the initial correspondence vectors described in Step~\ref{sec:step2}.
%This yields a significantly better initial location of the highly-nonconvex objective function and improves the computational efficiency, since much less coarse-to-fine pyramids are needed.
%
Figure~\ref{fig:deformationfield} shows some examples of deformation fields derived from the estimated shape flow computed by the aforementioned method. These results correspond to exemplar training shapes in the case of an arm dataset. We observe that the shape flow estimation captures the shape and deformations of the human arm in a plausible way.

@@
